\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
allows not allow
describe root as a framework, it's a program and a library

This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, written in Python and internally based on the Geant4 application 
programming interface (API) and the Geometry Description Markup Language (GDML) for file persistency~\cite{GDML}. The main features of \PYGEOMETRY{} 
are a Python scripting API to rapidly design parametrised geometry; conversion to and from  FLUKA geometry descriptions; conversion from CAD formats  (STEP 
and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE}; and powerful geometry visualisation tools based on VTK \cite{VTK4}. The 
origin of \PYGEOMETRY{} was a set of utilities to prepare geometry for an accelerator beamline simulation program based on Geant4 called BDSIM \cite{BDSIM_Nevay}. 
Accelerator physicists, like specialists in other areas, need a tool to quickly model specialist geometry and the subsequent interaction of the charged particle beam. 
\PYGEOMETRY{} allow the rapid creation and adaptation of geometry. Figure~\ref{fig:workflow} depicts various workflows possible with \PYGEOMETRY{}. \PYGEOMETRY{} 
is not an executable software package but a toolkit, a user would typically write a very small Python program to use to use the classes and functions provided by 
\PYGEOMETRY{}. This paper describes version 1.0 of \PYGEOMETRY{}, which is freely available as a git repository and via the Python Package Index (PyPi).

@@

There are existing codes that have functionality similar to \PYGEOMETRY{}. ROOT~\cite{Brun:1997pa}, the high-energy physics data analysis program, 
can load, display and manipulate GDML-like geometry. Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, commercial 
products include ESABASE2 \cite{ESABASE2} and FASTRAD \cite{FASTRAD}. There are also tools from the fusion and neutronics community that can convert CAD 
geometry into formats usable by MCRT codes examples include DAGMC~\cite{DAGMC} and McCAD~\cite{McCad}. In principle CAD software can export shape data to STL 
(or other similar mesh formats), which can be used by Geant4~\cite{poole2012acad}. In practice, using a lot of CAD models is difficult if a CAD model is comprised of a 
large number of parts. Exporting, assigning material to and placing the STL components into the MCRT can be a cumbersome task. The existent set of software does not 
provide a complete set of tools to efficiently create complex geometries.

>>>>

This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, written in Python and internally based on the Geant4 application 
programming interface (API) and the Geometry Description Markup Language (GDML) for file persistency~\cite{GDML}. The main features of \PYGEOMETRY{} 
are a Python scripting API to rapidly design parametrised geometry; conversion to and from  FLUKA geometry descriptions; conversion from CAD formats  (STEP 
and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE}; and powerful geometry visualisation tools based on VTK \cite{VTK4}. The 
origin of \PYGEOMETRY{} was a set of utilities to prepare geometry for an accelerator beamline simulation program based on Geant4 called BDSIM \cite{BDSIM_Nevay}. 
Accelerator physicists, like specialists in other areas, need a tool to quickly model specialist geometry and the subsequent interaction of the charged particle beam. 
\PYGEOMETRY{} allows the rapid creation and adaptation of geometry. Figure~\ref{fig:workflow} depicts various workflows possible with \PYGEOMETRY{}. \PYGEOMETRY{} 
is not an executable software package but a toolkit, a user would typically write a very small Python program to use to use the classes and functions provided by 
\PYGEOMETRY{}. This paper describes version 1.0 of \PYGEOMETRY{}, which is freely available as a git repository and via the Python Package Index (PyPi).

@@

There are existing codes that have functionality similar to \PYGEOMETRY{}. ROOT~\cite{Brun:1997pa}, the high-energy physics data analysis framework, 
can load, display and manipulate GDML-like geometry. Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, commercial 
products include ESABASE2 \cite{ESABASE2} and FASTRAD \cite{FASTRAD}. There are also tools from the fusion and neutronics community that can convert CAD 
geometry into formats usable by MCRT codes examples include DAGMC~\cite{DAGMC} and McCAD~\cite{McCad}. In principle CAD software can export shape data to STL 
(or other similar mesh formats), which can be used by Geant4~\cite{poole2012acad}. In practice, using a lot of CAD models is difficult if a CAD model is comprised of a 
large number of parts. Exporting, assigning material to and placing the STL components into the MCRT can be a cumbersome task. The existent set of software does not 
provide a complete set of tools to efficiently create complex geometries.
